---
title: "Business Intelligence Lab Submission Markdown"
author: "<Lakers>"
date: "<26/09/2023>"
output:
  github_document: 
    toc: yes
    toc_depth: 4
    fig_width: 6
    fig_height: 4
    df_print: default
editor_options:
  chunk_output_type: console
  markdown: 
    wrap: 72
---

# Student Details

|                                                   |                                                                                                                                                                                                                                                                                                                                                             |              |
|-----------------|---------------------------------------|-----------------|
| **Student ID Numbers and Names of Group Members** | 1. 135203 - C - Tom Arnold \| \| 2. 131749 - C - Teresia Nungari \| \| 3. 134780 - C - Trevor Augustine \| 4. 132840 - C - Sheila Wangui \| \| 5. ID - Class Group - Name \| |              |
|                                                   | **GitHub Classroom Group Name**                                                                                                                                                                                                                                                                                                                             | *\<Lakers\>* |
| **Course Code**                                   | BBT4206                                                                                                                                                                                                                                                                                                                                                     |              |
| **Course Name**                                   | Business Intelligence II                                                                                                                                                                                                                                                                                                                                    |              |
| **Program**                                       | Bachelor of Business Information Technology                                                                                                                                                                                                                                                                                                                 |              |
| **Semester Duration**                             | 21^st^ August 2023 to 28^th^ November 2023                                                                                                                                                                                                                                                                                                                  |              |

# Setup Chunk

We start by installing all the required packages

```{r Install Packages, echo=TRUE, message=FALSE, warning=FALSE}
## formatR - Required to format R code in the markdown ----
if (!is.element("formatR", installed.packages()[, 1])) {
  install.packages("formatR", dependencies = TRUE,
                   repos="https://cloud.r-project.org")
}
require("formatR")


## readr - Load datasets from CSV files ----
if (!is.element("readr", installed.packages()[, 1])) {
  install.packages("readr", dependencies = TRUE,
                   repos="https://cloud.r-project.org")
}
require("readr")
```

------------------------------------------------------------------------

**Note:** the following "*KnitR*" options have been set as the defaults
in this markdown:\
`knitr::opts_chunk$set(echo = TRUE, warning = FALSE, eval = TRUE, collapse = FALSE, tidy.opts = list(width.cutoff = 80), tidy = TRUE)`.

More KnitR options are documented here
<https://bookdown.org/yihui/rmarkdown-cookbook/chunk-options.html> and
here <https://yihui.org/knitr/options/>.

```{r setup, echo=TRUE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(
	eval = TRUE,
	echo = TRUE,
	warning = FALSE,
	collapse = FALSE,
	tidy = TRUE
)
```

------------------------------------------------------------------------

**Note:** the following "*R Markdown*" options have been set as the
defaults in this markdown:

> output:\
> \
> github_document:\
> toc: yes\
> toc_depth: 4\
> fig_width: 6\
> fig_height: 4\
> df_print: default\
> \
> editor_options:\
> chunk_output_type: console

# Loading the Student Performance Dataset

The 20230412-20230719-BI1-BBIT4-1-StudentPerformanceDataset is then
loaded. The dataset and its metadata are available here:
<https://drive.google.com/drive/folders/1-BGEhfOwquXF6KKXwcvrx7WuZXuqmW9q?usp=sharing>

```{library(readr)}
library(readr)
Student <- read_csv(
  "data/Student.csv",
  col_types = cols(
    class_group = col_factor(levels = c("A","B","C")),
    gender = col_factor(levels = c("0","1")),
    regret_choosing_bi = col_factor(levels = c("0","1")),
    drop_bi_now = col_factor(levels = c("0","1")),
    motivator = col_factor(levels = c("0","1")),
    read_content_before_lecture = col_factor(levels = c("0","1","2","3","4","5")),
    anticipate_test_questions = col_factor(levels = c("0","1","2","3","4","5")),
    answer_rhetorical_questions = col_factor(levels = c("0","1","2","3","4","5")),
    copy_new_terms_in_reading_notebook = col_factor(levels = c("0","1","2","3","4","5")),
    take_quizzes_and_use_results = col_factor(levels = c("0","1","2","3","4","5")),
    read_content_before_lecture = col_factor(levels = c("0","1","2","3","4","5")),
    reorganise_course_outline = col_factor(levels = c("0","1","2","3","4","5")),
    write_down_important_points = col_factor(levels = c("0","1","2","3","4","5")),
    space_out_revision = col_factor(levels = c("0","1","2","3","4","5")),
    studying_in_study_group = col_factor(levels = c("0","1","2","3","4","5")),
    schedule_appointments = col_factor(levels = c("0","1","2","3","4","5")),
    goal_oriented = col_factor(levels = c("0","1")),
    spaced_repetition = col_factor(levels = c("0","1","2","3","4","5")),
    testing_and_active_recall = col_factor(levels = c("0","1","2","3","4","5")),
    interleaving = col_factor(levels = c("0","1","2","3","4","5")),
    categorizing = col_factor(levels = c("0","1","2","3","4","5")),
    retrospective_timetable = col_factor(levels = c("0","1","2","3","4","5")),
    cornell_notes = col_factor(levels = c("0","1","2","3","4","5")),
    sq3r = col_factor(levels = c("0","1","2","3","4","5")),
    commute = col_factor(levels = c("0","1","2","3","4","5")),
    study_time = col_factor(levels = c("0","1","2","3","4","5")),
    repeats_since_Y1 = col_integer(),
    paid_tuition = col_factor(levels = c("0","1")),
    free_tuition = col_factor(levels = c("0","1")),
    extra_curricular = col_factor(levels = c("0","1")),
    sports_extra_curricular = col_factor(levels = c("0","1")),
    exercise_per_week = col_integer(),
    meditate = col_integer(),
    pray = col_integer(),
    internet = col_factor(levels = c("0","1")),
    laptop = col_factor(levels = c("0","1")),
    family_relationships = col_factor(levels = c("0","1","2","3","4","5")),
    friendships = col_factor(levels = c("0","1","2","3","4","5")),
    romantic_relationships = col_factor(levels = c("0","1","2","3","4","5")),
    spiritual_wellnes = col_factor(levels = c("0","1","2","3","4","5")),
    financial_wellness = col_factor(levels = c("0","1","2","3","4","5")),
    health = col_factor(levels = c("0","1","2","3","4","5")),
    day_out = col_integer(),
    night_out = col_integer(),
    alcohol_or_narcotics = col_factor(levels = c("0","1")),
    mentor = col_factor(levels = c("0","1")),
    mentor_meetings = col_integer()
  ))
View(Student)
```

## Description of the Dataset

We then display the number of instances in each class.

Student_class_group_freq <- Student$class_group
cbind(frequency = table(Student_class_group_freq),
      percentage = prop.table(table(Student_class_group_freq)) * 100)

Student_gender_freq <- Student$gender
cbind(frequency = table(Student_gender_freq),
      percentage = prop.table(table(Student_gender_freq)) * 100)

Student_regret_choosing_bi_freq <- Student$regret_choosing_bi
cbind(frequency = table(Student_regret_choosing_bi_freq),
      percentage = prop.table(table(Student_regret_choosing_bi_freq)) * 100)

Student_drop_bi_now_freq <- Student$regret_choosing_bi
cbind(frequency = table(Student_drop_bi_now_freq),
      percentage = prop.table(table(Student_drop_bi_now_freq)) * 100)

Student_motivator_freq <- Student$motivator
cbind(frequency = table(Student_motivator_freq),
      percentage = prop.table(table(Student_motivator_freq)) * 100)
```

Next we discover the mode of different variables

`Student_class_group_mode <- names(table(Student$class_group))[
  which(table(Student$class_group) == max(table(Student$class_group)))
]
print(Student_class_group_mode)

Student_gender_mode <- names(table(Student$gender))[
  which(table(Student$gender) == max(table(Student$gender)))
]
print(Student_gender_mode)

Student_regret_choosing_bi_mode <- names(table(Student$regret_choosing_bi))[
  which(table(Student$regret_choosing_bi) == max(table(Student$regret_choosing_bi)))
]
print(Student_regret_choosing_bi_mode)

Student_drop_bi_now_mode <- names(table(Student$drop_bi_now))[
  which(table(Student$drop_bi_now) == max(table(Student$drop_bi_now)))
]
print(Student_drop_bi_now_mode)

Student_motivator_mode <- names(table(Student$motivator))[
  which(table(Student$motivator) == max(table(Student$motivator)))
]
print(Student_motivator_mode)
```

# We find Kurtosis of each variable

Describe the code chunk here:

``if (!is.element("e1071", installed.packages()[, 1])) {
  install.packages("e1071", dependencies = TRUE)
}
require("e1071")
sapply(Student[, 10],  kurtosis, type = 2)
sapply(Student[, 33],  kurtosis, type = 2)


## ANOVA>


Student_one_way_anova <- aov( YOB ~ study_time, data = Student)
summary(Student_one_way_anova)

#Histogram
Student_YOB <- as.numeric(unlist(Student[, 4]))
hist(Student_YOB, main = names(Student)[4])


## \<You Can Have Another Sub-Title Here if you wish\>

```{r Your Eighth Code Chunk}
# Fill this with other R related code that will be executed when the R markdown
```

**etc.** as per the lab submission requirements. Be neat and communicate
in a clear and logical manner.
